### 2016-10-06 Documents/bootcamp_syllabus.tex
Small changes to syllabus -- Add words about code practice and project. (#15)

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them --- they're good practice ---
but your grade will be based on the best two.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

@@

\item {\bf Project.\/}
We work our way up to the project one step at a time, starting with idea generation and ending
with a {\bf professional piece of data collection and analysis\/}
that you can share with potential employers.
The structure of the project is laid out in a separate document.

>>>>

\item {\bf Code Practice.\/}
There are three such assignments in the first month.
We encourage you do to all of them --- they're good practice ---
but your grade will be based on the best two. We find that people who finish these assignments
tend to keep up with the material better and these are easy points to get in terms of grades.
We will also distribute Optional Code Practice ``assignments,''
but they will not be collected or graded.
They are, however, a good way to develop your coding skills.

@@

\item {\bf Project.\/}
We work our way up to the project one step at a time, starting with idea generation and ending
with a {\bf professional piece of data collection and analysis\/}
that you can share with potential employers.
The structure of the project is laid out in a separate document. We have found that the quality
of final project had a surprisingly low correlation to previous programming experience. A little thought and
effort go a long way in creating an interesting project.
